---
title: "my-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::knitr}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
devtools::install_github("Elaineflying/Assignment6", build_vignettes = TRUE)
library(knapsack)
```

### Create a random sample dataset called knapsack_objects for testing
```{r}
RNGversion(min(as.character(getRversion()),"3.5.3"))
set.seed(42, kind = "Mersenne-Twister", normal.kind = "Inversion")
n <- 2000
knapsack_objects <-
data.frame(
w=sample(1:4000, size = n, replace = TRUE),
v=runif(n = n, 0, 10000)
)
```

### Using Brute Force Search to solve knapsack problems
```{r}
brute_force_knapsack(x = knapsack_objects[1:8,], W = 3500)
```
```{r}
brute_force_knapsack(x = knapsack_objects[1:12,], W = 3500)
```
```{r}
brute_force_knapsack(x = knapsack_objects[1:8,], W = 2000)
```
```{r}
brute_force_knapsack(x = knapsack_objects[1:12,], W = 2000)
```
```{r}
brute_force_knapsack(x = knapsack_objects[1:16,], W = 2000)
```
Question How much time does it takes to run the algorithm for n = 16 objects?


### Using Dynamic Search to solve knapsack problems
```{r}
dynamic_knapsack(x = knapsack_objects[1:8,], W = 3500)
```
```{r}
dynamic_knapsack(x = knapsack_objects[1:12,], W = 3500)
```
```{r}
dynamic_knapsack(x = knapsack_objects[1:8,], W = 2000)
```
```{r}
dynamic_knapsack(x = knapsack_objects[1:12,], W = 2000)
```
```{r}
dynamic_knapsack(x = knapsack_objects[1:500,], W = 2000)
```
Question How much time does it takes to run the algorithm for n = 500 objects?


### Using Greedy Heuristic Search to solve knapsack problems
```{r}
greedy_knapsack(x = knapsack_objects[1:8,], W = 3500)
```
```{r}
greedy_knapsack(x = knapsack_objects[1:12,], W = 3500)
```
```{r}
greedy_knapsack(x = knapsack_objects[1:8,], W = 2000)
```
```{r}
greedy_knapsack(x = knapsack_objects[1:12,], W = 2000)
```
```{r}
greedy_knapsack(x = knapsack_objects[1:500,], W = 2000)
```
Question How much time does it takes to run the algorithm for n = 1000000 objects?


### Profile code using profvis package

Question What performance gain could you get by trying to improving your code?


### Implementation code in Rcpp

Question What performance gain could you get by using Rcpp and C++?
